\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage{mathpazo}
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=blue!70!black
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Kevin Joseph}} & Email: \href{mailto:josephkevin1995@gmail.com}{josephkevin1995@gmail.com} \\
  \href{https://josephkevin.dev}{Website: josephkevin.dev} & Mobile: +1 (516) 395-5190 \\
\end{tabular*}

%----------SUMMARY-----------------
\vspace{4pt}
Front-end engineer with 7+ years of experience building responsive, performant web apps in Angular, TypeScript, focused on shipping accessible UIs that improve engagement and conversion
%-----------SKILLS-----------------
\vspace{-5pt}
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages \& Frameworks}{Angular, TypeScript, JavaScript, RxJS, HTML, SCSS, CSS, Storybook, Nx}
    \resumeSubItem{Testing}{Jest, Jasmine, Karma, Spectator, ng-mocks}
    \resumeSubItem{Backend \& APIs}{REST API Design, PostgreSQL}
    \resumeSubItem{Real-time \& Integrations}{Microsoft SignalR (WebSocket), Datadog}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\vspace{-5pt}
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Banner Life Insurance}{ 2018 -- Present}
      {Application Engineer}{2020 -- Present}
      \resumeItemListStart
        \item Co-founded and grew an Angular component library to 50+ reusable components shared across all Horizon applications, built with Angular and Storybook.
        \item Architected and delivered four specialized frontend micro-libraries: IAM (authentication/authorization), Errors (global error handling), Metrics (logging and Datadog integration), and WebSocket (real-time communication via Microsoft SignalR).
        \item Co-led migration of all frontend libraries and applications into a unified Nx monorepo, standardizing tooling, improving code sharing, and streamlining CI/CD across the platform.
        \item Led migration of the test suite from Karma/Jasmine to Jest, improving test execution speed and developer experience across the monorepo.
        \item Adopted ng-mocks to simplify Angular dependency mocking, reducing test boilerplate and improving test maintainability at scale.
        \item Maintained greater than 80\% code coverage and enforced Sonar Way quality standards across all projects using SonarQube.
        \item Engineered a full-lifecycle customer portal (Skyline) in Angular/NgRx; enabled policyholders to manage applications mid-journey and monitor payments, with a target adoption rate of 25\% by end of 2026.
      \resumeItemListEnd
    \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{Associate Application Engineer} & \textit{ 2018 -- 2020} \\
    \end{tabular*}\vspace{-5pt}
      \resumeItemListStart
        \item Led frontend development of a rules-driven Angular application replacing a paper-based life insurance process, driving instant decision rates from under 4\% to 46\% and exam-free application rates from 0\% to 80\%.
        \item Developed an internal Application Manager dashboard enabling underwriters to manage assigned cases and auto-generated tasks, digitizing the post-submission review workflow and  reducing average underwriting cycle time from 50+ days to \textasciitilde11 days.
        \item Extended the Application Manager to serve external insurance agents, providing real-time visibility into submitted application status.
        \item Developed a Telephonic Interview application enabling phone-based agents to complete applications on behalf of clients via SSO, including guided call script UX enhancements.
        \item Established unit testing practices using Karma, Jasmine, and Spectator, laying the foundation for a culture of quality that later scaled to $\geq$80\% coverage across the platform.
        \item Built a suite of applications that achieved 99.9\% digital adoption by early 2025, a 5\% increase in policy placement rate, user satisfaction growth from \textasciitilde35\% to \textasciitilde50\%, and 88\% electronic policy delivery.
      \resumeItemListEnd
    \vspace{-5pt}
    \resumeSubheading{Zoho Corp.}{Full-time}
      {Member Technical Staff}{ 2017 - 2018}
      \resumeItemListStart
        \item Spearheaded early data modeling efforts for \href{https://www.zoho.com/contracts/}{Zoho Contract Management} using PostgreSQL, reducing data redundancy by 20\% and optimizing query performance for faster contract retrieval.
        \item Collaborated within a thirteen-member team to implement the data model and APIs using PostgreSQL, Java, and an internal Zoho framework.
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% %-----------PROJECTS-----------------
% \vspace{-5pt}
% \section{Academic Projects}
%   \resumeSubHeadingListStart
%     \resumeSubItem{Playing Atari Games using Reinforcement learning (B.Tech Final Project)}{Research oriented project based on paper: \href{https://arxiv.org/pdf/1312.5602.pdf}{https://arxiv.org/pdf/1312.5602.pdf} by the Deep Mind team at Google. Built a program that could achieve super human performance in atari games using Q-learning and convolutional neural networks.}
%     \vspace{2pt}
%     \resumeSubItem{Indoor Navigation system using Bluetooth Low Energy (BLE) tags}{Indoor navigation system that featured an AngularJS based admin panel to upload and configure maps and an android application for users to navigate on the map. The system was made for use within large malls or hospitals.}
%     \vspace{2pt}
%     \resumeSubItem{IEEE LINK App}{A Social networking application built for IEEE Local Integrated Network for Kerala (LINK) IEEE students.}
%     \vspace{2pt}
%     \resumeSubItem{Face-detection and photography rover}{An automated face detection and photography rover built for automated photography at events. It was built using a raspberry pi board and an android phone. It was deployed during a technical event at College of Engineering Trivandrum in 2014 and took 7000+ photos.}
%   \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\vspace{-5pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {College of Engineering Trivandrum (University of Kerala)}{Thiruvananthapuram, India}
      {Bachelor of Technology - Computer Science and Engineering}{2013 - 2017}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\vspace{-5pt}
\section{Awards and Certifications}
  \begin{description}[font=$\bullet$]
    \item \href{https://www.computer.org/volunteering/awards/scholarships/merwin/merwin-winners/2016-merwin-winners}{Richard E. Merwin Scholarship} - September, 2016
    \vspace{-5pt}
    \item \href{https://www.coursera.org/learn/machine-learning}{Coursera Machine Learning certification} by Stanford with 97.6\% score
    \vspace{-5pt}
    \item \href{https://www.coursera.org/learn/algorithmic-toolbox}{Coursera Algorithmic toolbox certification} by UC San Diego with 100\% score
    \vspace{-5pt}
    \item \href{https://www.scrumalliance.org/get-certified/scrum-master-track/certified-scrummaster}{Scrum Alliance certified scrum master}
  \end{description}

% \vspace{-5pt}
% \section{Volunteer Experience}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {IEEE Computer Society Student Ambassador}{2017}
%       {Functioned as a liaison between IEEE Computer Society Geographic Activities Board and student members}{}
%       \vspace{5pt}
%     \resumeSubheading
%       {IEEE Student branch technical coordinator}{2016}
%       {Organized college level technical events to encourage students to learn applied CS by building real world projects}{}
%       \vspace{5pt}
%     \resumeSubheading
%       {Local organizing team member: International workshop on Internet of Things}{2016}
%       {Two day technical on Internet of Things by \href{https://www.linkedin.com/in/soumya-kanti-datta-0907133b/?originalSubdomain=fr}{Soumya Kanti Datta}}{}
%       \vspace{5pt}
%     \resumeSubheading
%       {Google student Facilitator for Applied Computer Science}{2016}
%       {Taught and Facilitated a course on android app development by Google at College of Engineering Trivandrum}{}
%       \vspace{5pt}
%     \resumeSubheading
%       {IEEE Computer Society Student Chapter Vice Chair}{2015}
%       {Organized events, conducted and delivered workshops on applied computing skills for IEEE CS branch members.}{}
%       \vspace{5pt}
%     \resumeSubheading
%       {Organizing team member: IEEE Computer Society India Symposium}{2015}
%       {First national level flagship technical event for Computer Society India}{}
%   \resumeSubHeadingListEnd

\end{document}
